Subsegmental language detection in Celtic language text

### 2014-05-09 codeswitch-cltw-2014/codeswitch.tex
related work
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@52712 72bbbca6-d526-0410-a7d9-f06f51895060

>>>>

\section{Related Work}
\label{sec:relwork}

There has been significant research on code-switching and segment detection problems. The good thing about multilingual code switched data is that there are differences in the words of different languages - phonologically, morphologically, lexically and syntactically. At least that is the case with the pairs of languages we have chosen according to their usage in common day scenario. \\

Before the Internet era, this study was focussed more on speech data. Initial research on this code switching was done for Marathi and English \cite{joshi1982processing} which included notable work about the formalisms and parsing. \\

It is seen that language modelling techniques have shown promise earlier, such as in \cite{yu2013identification} the experiment on Mandarin-Taiwanese code-switched sentences show a high accuracy in terms of detecting code-switched sentences. \\

Our idea of going to character level inspection has been inspired both by the language modelling techniques used by the community as well as the acoustic modelling research. From \cite{chan2004detection} which has made use of the bi-phone probabilities and calculated them to measure a confidence metric, to \cite{lyu2006language} which has made use of a classification method, named syllable-based duration classification, which uses the tonal syllable properties along with the speech signals to help predict the code switch points. \cite{yeong2010language} uses syllable structure information, and increases our confidence is using the character n-gram approach for detection of the code switching points, their study was for the Malay-English, identifying the language of the words in the code switched data set.\\
